---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(cpp11)
Sys.setenv(
  PKG_CXXFLAGS = paste0("-I", getwd(), "/dist/include -I/opt/homebrew/opt/openssl@1.1/include"),
  PKG_LIBS = paste0("-L/opt/homebrew/opt/openssl@1.1/lib -lssl -lcrypto -L", getwd(), "/dist/lib -ls2geography -ls2 -labsl_base -labsl_city -labsl_demangle_internal -labsl_flags_reflection -labsl_graphcycles_internal -labsl_hash -labsl_hashtablez_sampler -labsl_int128 -labsl_low_level_hash -labsl_malloc_internal -labsl_raw_hash_set -labsl_raw_logging_internal -labsl_spinlock_wait -labsl_stacktrace -labsl_str_format_internal -labsl_strings -labsl_symbolize -labsl_synchronization -labsl_throw_delegate -labsl_time_zone -labsl_time")
)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# s2geography

<!-- badges: start -->
<!-- badges: end -->

## Usage

s2geography depends on [s2geometry](https://github.com/google/s2geometry), which depends on [Abseil](https://github.com/abseil/abseil-cpp) and OpenSSL. If you already have a project that uses s2geometry, you should probably just copy the contents of the src/ directory into your project and `#include "s2geography.hpp"` when needed.

Otherwise you can build and install using `cmake`. The project is structured such that the VSCode `cmake` integration "just works" (if it doesn't, consider adding `CMakeUserPresets.json` to configure things like the install directory or location of OpenSSL). You can also configure manually:

```bash
git clone https://github.com/paleolimbot/s2geography.git s2geography
mkdir s2geography/build && cd s2geography/build

# you may need to specify the location of OpenSSL
# (e.g., `cmake .. -DOPENSSL_ROOT_DIR=/opt/homebrew/opt/openssl@1.1` on M1 mac)
cmake ..
cmake --build .
cmake --install . --prefix ../dist
```

This will also download, build, and install Abseil and s2geometry to the install directory. By default this will build and install static libraries for s2geography, s2, and many abseil libraries. If you are building your own project with CMake, you should be able to do:

```cmake
include(FetchContent)
FetchContent_Declare(
  s2geography
  GIT_REPOSITORY https://github.com/paleolimbot/s2geography.git
  GIT_TAG <PICK A COMMIT SHA1>
  GIT_SHALLOW TRUE)
FetchContent_MakeAvailable(s2geography)
```

Otherwise, you can add some compier/linker flags and `#include "s2geography.hpp"`. This will also let you `#include` any/all of s2geometry.

```
CPPFLAGS = -I<install_prefix>/include -I<openssl_root_dir>/include
LDFLAGS = -L<openssl_root_dir>/lib -lssl -lcrypto -L<install_prefix>/lib -ls2geography -ls2 -labsl_base -labsl_city -labsl_demangle_internal -labsl_flags_reflection -labsl_graphcycles_internal -labsl_hash -labsl_hashtablez_sampler -labsl_int128 -labsl_low_level_hash -labsl_malloc_internal -labsl_raw_hash_set -labsl_raw_logging_internal -labsl_spinlock_wait -labsl_stacktrace -labsl_str_format_internal -labsl_strings -labsl_symbolize -labsl_synchronization -labsl_throw_delegate -labsl_time_zone -labsl_time
```

Somebody who is better than me at `cmake` could probably do a better job making the CMake build more flexible and/or get shared libraries to work.

# Example

A quick example (using R and the [cpp11](https://cpp11.r-lib.org/) package) (using `Sys.setenv()` to set the `PKG_CXXFLAGS` and `PKG_LIBS` environment variables to the `CPPFLAGS` and `LDFLAGS`)

```{cpp11}
#include "cpp11.hpp"
#include "s2geography.hpp"

using namespace s2geography;

[[cpp11::register]]
void test_s2geography() {
  PointGeography point1 = S2LatLng::FromDegrees(45, -64).ToPoint();
  PointGeography point2 = S2LatLng::FromDegrees(45, 0).ToPoint();
  
  ShapeIndexGeography point1_index(point1);
  ShapeIndexGeography point2_index(point2);
  
  double dist = s2_distance(point1_index, point2_index);
  
  Rprintf("distance result is %g", dist);
}
```

```{r}
test_s2geography()
```
